Autonomous Aerial Exploration for Topological Mapping of Mars Environments

### 2018-06-11 Conference/SCITECH19/SCITECH19.tex
added close-up figures

The simulation was run twice. Case 1 was as described in this paper. Case 2 was identical to Case 1, except the reduced map $ m_\text{reduced}$ is used when computing \refeqn{Iscan}. Case 2 is largely inspired by the promising results of~\cite{KauTakAiLee18}, where a projected map based on the same criteria as \refeqn{Proj3DMapComb} proved effective for level flight. The resulting occupancy grid maps for Case 1 and 2 are shown in Figs. \ref{fig:mars3DogmCase1} and \ref{fig:mars3DogmCase2}, respectively, and complete map entropy is illustrated in Fig. \ref{fig:mars3Dentropy}.

@@

@@

\todo{I wish we have a little more pages. We can have another zoomed-in figure hat shows the aerial vehicle with the simulated measurements of the point clouds and the candidate poses more clearly}

>>>>

The simulation was run twice. Case 1 was as described in this paper. Case 2 was identical to Case 1, except the reduced map $ m_\text{reduced}$ is used when computing \refeqn{Iscan}. Case 2 is largely inspired by the promising results of~\cite{KauTakAiLee18}, where a projected map based on the same criteria as \refeqn{Proj3DMapComb} proved effective for level flight. The resulting occupancy grid maps for Case 1 and 2 are shown in Figs. \ref{fig:mars3DogmCase1} and \ref{fig:mars3DogmCase2}, respectively, and close-up pictures from Case 2 are shown in \ref{fig:marsZoomedIn}. The complete map entropy is illustrated in Fig. \ref{fig:mars3Dentropy}.

@@

\begin{figure}[!t]
	\centering
	\begin{subfigure}[t]{0.95\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{mars_closeup.png}
        		\caption{Full Map Cells and Sensor Scan}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
	\centering
	\begin{subfigure}[t]{0.95\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{scitech_reducedCells.png}
        		\caption{Full Map and Reduced Map Cells}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
\caption{The close-up images from the Case 2 trial show the candidate future poses (red arrows), where greater opacity represents a larger objective function of \refeqn{CandidateLocationOptimization}. In (a), we show the 3D scan with color corresponding to the surface of Mars. In (b), we overlay the full map $m$ (colored) with the reduced map $m_\text{reduced}$ (gray).}
\label{fig:marsZoomedIn}
\end{figure}

@@
